### 2025-04-15 docs/Homeownership_BankOfMomAndDad.tex
Include marriage and non-winsorized data in regressions

I run an ordinary least squares (OLS) regression on house purchase values for first-time owners and test whether lagged parental wealth (logged) is positively associated with larger house purchases $(\beta_1)$, controlling for lagged log income, lagged log net worth, education, age, log household size, regions, time, and race:
\begin{equation*}
\ln{HVal_{i}} = \beta_1 \ln(Wealth)_{p(i),t-2} + \beta_2 \ln(Inc_{i,t-2}) + \beta_3 \ln(NetWorth_{i,t-2}) + \mathbf{\gamma}{X_{i,t}} + \varepsilon_{i}.
\end{equation*}
Parents' wealth, as well as household income and net worth, are log-transformed. Households are denoted by $i$ and their parents by $p(i)$. First-time buyers are households who have never been observed as homeowners before.

>>>>

I run an ordinary least squares (OLS) regression on house purchase values for first-time owners and test whether lagged parental wealth (logged) is positively associated with larger house purchases $(\beta_1)$, controlling for lagged log income, lagged log net worth, education, age, log household size, marriage, state, time, and race:
\begin{equation*}
\ln{HVal_{i}} = \beta_1 \ln(Wealth)_{p(i),t-2} + \beta_2 \ln(Inc_{i,t-2}) + \beta_3 \ln(NetWorth_{i,t-2}) + \mathbf{\gamma}{X_{i,t}} + \varepsilon_{i}.
\end{equation*}
Parents' wealth, as well as household income and net worth, are log-transformed. Households are denoted by $i$ and their parents by $p(i)$. First-time buyers are households who have never been observed as homeowners before.
